2-factor-Hull-White\_model\_calibration

### 2020-04-26 week5/Report.tex
Added Part 1 to the Report

\title{Price a European Up-and-out Call Option}

@@

\date{April. 8, 2020} % if this is omitted, the current date is used for the title page
\maketitle

\noindent
\textbf{Keywords:} Exotic Options, European up-and-out call option,  Black-Scholes-Merton model and Geometric Brownian Motion.

% the following creates an abstract -- it can be omitted
% an example of an environment: these have the form \begin{name} ... \end{name}
\begin{abstract}
This report presents the results of the simulation of a European up-and-out call option over twelve months.  The Black-Scholes-Merton model will be used to implement Monte Carlo estimations using Python code. The estimations will simulate paths for the underlying share and the counterparty's firm value using varying sample sizes, and determine estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA). Following from these it is simple to price the option incorporating counterparty risk, given by the default-free price less the CVA.
\end{abstract}

\section{Introduction
}
A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.  The payoff of an up-and-out option at maturity $T$ is given by,

\[
Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
\]
Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.  This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level. \\

The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.  This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}. Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.

Possible paths for the up-and-out barrier option payoff would look similar to the chart below, where two of the paths have crossed the barrier and resulted in zero payoff, but the other three have not crossed the barrier and behave like a vanilla option.

\begin{figure}
    \centering
    \caption{Simulated Payoffs for an Up-and-out Barrier Option}
    \includegraphics{images/barrier-example.png}
\end{figure}

We initialize most variables as given by the question. We assume the
counterparty firm's value is at 200, as this is above the counterparty's
debt due in one year. Also, we calculate the default-free value of our
option to be 6.60, so we select a firm value not too distant such that
the CVA value we calculate is not negligible. For example, if we chose
counterparty firm value as 1,000, the CVA would be 0.000.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{} Initialize problem parameters}
\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1} \PY{c+c1}{\PYZsh{} option maturity}
\PY{n}{L} \PY{o}{=} \PY{l+m+mi}{150} \PY{c+c1}{\PYZsh{} up\PYZhy{}and\PYZhy{}out barrier}
\PY{n}{S0} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} current share price}
\PY{n}{K} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} strike price, at\PYZhy{}the\PYZhy{}money}
\PY{n}{risk\PYZus{}free} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{08} \PY{c+c1}{\PYZsh{} risk\PYZhy{}free rate}
\PY{n}{sigma} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{3} \PY{c+c1}{\PYZsh{} volatility}
\PY{n}{v\PYZus{}0} \PY{o}{=} \PY{l+m+mi}{200} \PY{c+c1}{\PYZsh{} counterparty firm current value (Our assumption) }
\PY{n}{sigma\PYZus{}firm} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{25} \PY{c+c1}{\PYZsh{} volatility for the counterparty\PYZsq{}s firm}
\PY{n}{debt} \PY{o}{=} \PY{l+m+mi}{175} \PY{c+c1}{\PYZsh{} counterparty\PYZsq{}s debt, due in one year }
\PY{n}{corr} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{2} \PY{c+c1}{\PYZsh{} correlation}
\PY{n}{recovery\PYZus{}rate} \PY{o}{=} \PY{l+m+mf}{0.25} \PY{c+c1}{\PYZsh{} recovery rate}
\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}}
\PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

\section{Simulated Paths for the Underlying Share and Counterparty Firm
}

 In order to simulate paths for the underlying share and the firm,  we use a Cholesky decomposition to generate the correlated price paths.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{3}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}

    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
\end{Verbatim}
\end{tcolorbox}

    To double check that the stock prices and firm values monthly returns
are correlated, we check them as follows, generating 20 different price
paths with 10,000 timesteps.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{10000}\PY{p}{)}

\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}

\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}
    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Pearson correlation coefficient : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{, Two\PYZhy{}tailed p\PYZhy{}value }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

>>>>

\title{Price a Vanilla European Call Option}

@@

\date{April. 26, 2020} % if this is omitted, the current date is used for the title page
\maketitle

\noindent
\textbf{Keywords:} European Options, Heston model,  Constant Elasticity of Variance (CEV) model and Stochastic Volatility.

% the following creates an abstract -- it can be omitted
% an example of an environment: these have the form \begin{name} ... \end{name}
\begin{abstract}
    In this paper, we price a vanilla European call option under the Heston model and then simulate the monthly share price over a year using the Constant Elasticity of Variance (CEV) model, with the assumption of constant volatility each month. Monte Carlo simulations with varying sample sizes are run and the results are plotted against the closed form value for comparison.
\end{abstract}

\section{Introduction
}
We initialize most variables as given by the question.

\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The current share price is \$100
    \item The risk-free continuously compounded interest rate is 8%
    \item The volatility for the underlying share is 30%
\end{itemize}

\section{Fourier pricing technique under Heston model dynamics
}

Black-Scholes option pricing models assumed volatility of the underlying assets to be constant or a predetermined function of time, we will now implement a model which features instantaneous variance of asset price using volatility that evolves stochastically in time. Although there are several models incorporating stochastic volatility including introduced by Hull and White \cite{HW1}, Stein and Stein \cite{SS1} and Heston \cite{Heston1} \cite{Heston2}, we will implement Heston's constant interest rate model.

With the assumption that the underlying share follows the Heston model dynamics, the additional parameters required are specified as follows:
\begin{itemize}
    \item $\nu_0 = 0.06$
    \item $\kappa = 9$
    \item $\theta = 0.06$
    \item $\rho = -0.4$
\end{itemize}

    The Characteristic function is implemented using a function presented by
Albrecher et al \cite{AMST1}. The function is written as:
\[\phi_{S_T} = exp(C(\tau;u)+D(\tau;u)v_t + iu \log(S_t) )\]

Where,

\[C(\tau;u) = ri\tau u + \theta \kappa [\tau x\_ - \frac{1}{a}\log(\frac{1-ge^{d\tau}}{1-g})],\]

\[D(\tau;u) = (\frac{1-e^{d\tau}}{1-ge^{d\tau}})x\_,\]

\[\tau = T -t ,\]

\[ g = \frac{x\_}{x_+},\]

\[ x_\pm = \frac{b\pm d}{2a},\]

\[ d = \sqrt{b^2 - 4ac},\]

\[ c = - \frac{u^2 + ui}{2},\]

\[ b = \kappa - \rho \sigma iu,\]

\[ a = \frac {\sigma^2}{2}\]

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Characteristic function code}

\PY{n}{a} \PY{o}{=} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}

\PY{k}{def} \PY{n+nf}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{kappa} \PY{o}{\PYZhy{}} \PY{n}{rho}\PY{o}{*}\PY{n}{sigma}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}

\PY{k}{def} \PY{n+nf}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{u}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{+}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}

\PY{k}{def} \PY{n+nf}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{\PYZhy{}}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{a}\PY{o}{*}\PY{n}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{+}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{n}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{n}{val1} \PY{o}{=} \PY{n}{T}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{a}
    \PY{k}{return} \PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u} \PY{o}{+} \PY{n}{theta}\PY{o}{*}\PY{n}{kappa}\PY{o}{*}\PY{n}{val1}

\PY{k}{def} \PY{n+nf}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{n}{val1} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
    \PY{n}{val2} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
    \PY{k}{return} \PY{p}{(}\PY{n}{val1}\PY{o}{/}\PY{n}{val2}\PY{p}{)}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)} \PY{o}{+} \PY{n}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{v0} \PY{o}{+} \PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{adj\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}\PY{o}{/}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    Now we vectorize the code, calculate an estimate for integrals and
calculate the Fourier estimate of our call price.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{delta\PYZus{}t} \PY{o}{=} \PY{n}{t\PYZus{}max}\PY{o}{/}\PY{n}{N}
\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,}\PY{n}{N}\PY{p}{,}\PY{n}{N}\PY{p}{)}
\PY{n}{t\PYZus{}n} \PY{o}{=} \PY{p}{(}\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}

\PY{c+c1}{\PYZsh{}Integral calculations}
\PY{n}{first\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{adj\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
\PY{n}{second\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}

\PY{c+c1}{\PYZsh{}Call value}
\PY{n}{fourier\PYZus{}call\PYZus{}val} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{first\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{second\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}
\PY{n}{fourier\PYZus{}call\PYZus{}val}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
13.734895692109077
\end{Verbatim}
\end{tcolorbox}

    To see the effectiveness of the pricing option under Heston dynamics we
will also price the call option under Black-Scholes assumption.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} Code for analytical solution for vanilla European Call option}
\PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{o}{/}\PY{n}{K}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{r} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}
\PY{n}{d\PYZus{}2\PYZus{}stock} \PY{o}{=} \PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}

\PY{n}{analytic\PYZus{}callprice} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}1\PYZus{}stock}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}2\PYZus{}stock}\PY{p}{)}
\PY{n}{analytic\PYZus{}callprice}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
15.711312547892973
\end{Verbatim}
\end{tcolorbox}

\section{Simulate a share price path using CEV Model
}

\section{Monte Carlo estimates}

\section{Conclusion}
